%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{BHARGAV J. BHATT} % Your name
\address{+41 786 492 693 \\ bhargo360@gmail.com}  % Your phone number and email
\address{A007-2 Furst-Franz-Josef-Str. 15, Vaduz 9490, Liechtenstein} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{27th February 1992 \\ Indian}  % Your birth date and nationality

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{To enhance my working capacities for complex Database Systems, analytical skills and to seek
challenges with an opportunity for growth and career advancement as Data Scientist.}


\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{POSITION OF RESPONSIBILITY}

\begin{rSubsection}{Java Software Engineer - Student Assistant}{September 2017 - January 2019} 
{Functional Genomics Center Zurich, Switzerland} 
{\\Worked in the Data Integration team. Was part of development, implementation, maintenance and deployment of FGCZ content management and data retrieval system B-Fabric. It had 3 running instances and achieved CHF 1 million revenue as license fee.}
\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{Software Engineer}{April 2015 - July 2016} 
{INDIANIC, India} 
{\\Worked in configure.it team, an all in one development web platform for Android and IOS along with back-end support. IndiaNIC is a renowned company serving the IT industry over decades of years of experiences providing IT solutions for enterprise mobility, iPhone and Android apps development with more than 400 employees and presence in 7 countries worldwide.} 
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Java EE &  Java Servlet, EJB, JPA, JSF, JSP, EL, JAXB, JAX-WS, Java Mail, Hibernate\\
Programming Languages & PYTHON, C, PHP, SQL, SWIFT\\ 
Frameworks & JBoss Seam, Maven, Lucene, Flink, Spark, Kafka, Hadoop, MapReduce\\
Tools & Eclipse, Android Studio, PostgreSQL, IntelliJ, PyCharm, X-code\\
Web Technologies & HTML, CSS, XML, PrimeFaces, RichFaces\\
Web Tools & Adobe Dreamviewer, WordPress \\
Design Tools & Adobe Muse, Adobe Premier, CorelDraw X6, Photoshop CS6 \\
Version Control Systems & Subversion, GIT\\
Languages & English(IELTS 6.5), German(A2), Gujarati(Native), Hindi, Marathi, \\&French(basics), Sanskrit
\end{tabular}

\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
{\bf Master of Information System in Data Science} \hfill {September 2018 - Current}
\\ 
University of Liechtenstein, Vaduz, Liechtenstein. (Master continued)

{\bf Master of Informatics in Data Science} \hfill {February 2017 - August 2018}
\\ 
University of Zurich, Zurich, Switzerland.(3 Semester)

{\bf Bachelor of Computer Engineering} \hfill {June 2010 - May 2014}
\\ 
Sigma Institute of Engineering, Vadodara, Gujarat, India.
\\
Gujarat Technological University,  CGPA: 7.04/10.00

\end{rSection}

\begin{rSection}{Hobbies} \itemsep -1pt {}   
\item Exploring world, Capturing memories, Internet surfing, Reading, Music.
\end{rSection}
 

\pagebreak
\begin{rSection}{PROJECTS}
\begin{rSubsection}{Operations Analytics for Product Centered Firms \\Implications of GDPR for DSS
}{February 2018 - May 2018}{Big Data Law and Technology Project, University of Zurich}{} 
\item Effects of GDPR on software companies.
\end{rSubsection} 
\begin{rSubsection}{Stream Processing}{December 2017 - February 2018}{Master Basis Module, University of Zurich}{} 
\item To get insight of stream processing with help of Apache Flink, Apache Kakfa and Apache Spark
\end{rSubsection} 
\begin{rSubsection}{Semantic Analysis of Tweets}{March 2017 - June 2017}{Advance Software Engineering Project, University of Zurich}{} 
\item To get insight of Elasticity in Cloud computing. Semantic Analysis of tweets using specific hashtags 
\end{rSubsection} 
\begin{rSubsection}{US Food Recall-Analysis}{March 2017 - June 2017}{Big Data Analytics Project, University of Zurich}{} 
\item Time Series Analysis, Time Gap Analysis, Time patterns in the data.
\end{rSubsection} 
\begin{rSubsection}{Seeker’s Stop, Android Project}{May 2013 - May 2014}{Bachelor Thesis, Sigma Institute of Engineering, Vadodara, India}{} 
\item An Android platform to connect users and create a platform where one user acts as seeker that are the source of resources and another user acts as expert who can provide skills by their choice.
\end{rSubsection} 
\end{rSection} 

\begin{rSection}{SEMINARS}
\begin{rSubsection}{Recycling/Reutilisation of Ivoclar Vivadent’s Ceramic Shell - Discs
}{September 2018 - January 2019}{Bhargav Bhatt, Corina Chihai, Tobias K{\"o}gl, Christian Szabo, Elison Vrioni}{\\Innovation Lab I, University of Liechtenstein} 
\item Business proposal for managing waste materials.
\end{rSubsection} 
\begin{rSubsection}{An Overview of Emerging Wireless Communication Systems in 5G
}{February 2018 - May 2018}{Ananya Pandya, Bhargav Bhatt}{\\Communication System, University of Zurich}
\item The paper describes an emerging technologies of fifth generation wireless communication systems.
\end{rSubsection} 
\begin{rSubsection}{Comparative Analysis on Cryptocurrencies as Financial Assets.
}{September 2017 - December 2017}{Ananya Pandya, Bhargav Bhatt, Simon M\"uller, Vasileios Koukoutsas}{\\Internet Economics, University of Zurich}
\item The paper describes comparative analysis of four different cryptocurrencies
\end{rSubsection} 
\end{rSection} 

%----------------------------------------------------------------------------------------
%\begin{rSection}{Extra-Cirrucular Activities} \itemsep -1pt {}   
%\item Attended IIM Chaos, Ahmedabad, India \hfill December 2013 \& 2015
%\item Participated in Robo Race in College festival, India \hfill March 2012
%\item Attended IIT Bombay Techfest, Mumbai, India \hfill January 2012
%\end{rSection}

\end{document}
